### 2023-11-17 main.tex
Update main.tex

%In this notation, the elements of the duality matrix reads
%\begin{equation}\label{ElementsDualityMatrixChain_1}
%	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
%\end{equation}
%\\
Using duality, one can compute the  $m$-point correlations between non-empty particles in terms of the absorption probabilities of $m$ dual particles. Therefore, to determine the non-equilibrium steady state correlations of the integrable multi-species stirring process, it is enough to compute these absorption probabilities.  %For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$. 
\begin{proposition}[Correlations via duality]
\label{prop-absorbing}
Consider $m\in \{1,\ldots,L\}$ and let $a_{k}\in\{1,\ldots,N-1\}$ species positioned at sites $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$. Then, the $m$-point correlations in the non-equilibrium steady state (NESS) read
\begin{equation}
\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m})
\end{equation}
where
\begin{equation}\label{absProbabilitiesIntegrable}
	\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\bm{\xi}\right)
\end{equation}
is the  probability that  $t_{k}$ dual particles of species $a_{k}$ (initially positioned at site $x_{k}$) are absorbed at the extra site $\{0\}$. The dual initial configuration is $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that 
\begin{equation}
\label{xsi-init}
	\begin{cases}
		\xi_{a}^{x}=1\qquad \text{if}\;x=x_{k}\;\text{and}\; a=a_{k}\\
		\xi_{a}^{x}=0\qquad \text{otherwise}
	\end{cases}
\end{equation}
\end{proposition}
\textbf{Proof}:
For any $\bm{\tau}\in \Omega$ the duality matrix defined in \eqref{ElementsDualityMatrixChain_1} evaluated on the dual configuration $\bm{\xi}\in\widetilde{\Omega}$ given in \eqref{xsi-init} read
\begin{equation}
	D(\bm{\tau},\bm{\xi})%=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{x_{k}},a_{k}}=1\}}
	=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\dt
\end{equation}
Therefore, by duality and ergodicity we have 
\begin{equation}\label{CorrelationByABS-prob}
	\begin{split}
\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})\dt
\end{split}
\end{equation}
\begin{flushright}
	$\square$
\end{flushright}

@@

\begin{theorem}[Explicit non-equilibrium steady state correlations]\label{thm-correlations}

@@

	\langle W|\widetilde{X}_{N}^{n_{N}}|V\rangle&=\langle W|\widetilde{X}_{N}\widetilde{X}_{N}^{n-1}|V\rangle=\langle W|\widetilde{X}_{N}^{n-1}|V\rangle +\langle W|\frac{1}{(\alpha_{a}-\beta_{a})}\widetilde{X}_{a}\widetilde{X}_{N}^{n-1}|V\rangle

@@

	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}=\frac{\Gamma(2+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})}{\Gamma(1+\sum_{j=x}\delta_{\tau_{j},N})}

@@

=&\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\frac{\Gamma(2+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})}{\Gamma(1+\sum_{j=x}\delta_{\tau_{j},N})}\nonumber\\

@@

		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau},\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\frac{1}{(L+1)!}\prod_{x=1}^L\left((\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}(1-\delta_{\sigma_{j},N})\right)\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]%\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\\&+

@@

\begin{remark} By change the summation indices form $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}\in \{0,1-\delta_{\tau_{x},N}\}$ and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as 

@@

	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) =\left(2+L-y-\sum_{j=x}^{L}(1-\delta_{\tau_{x},N})\right)

@@

\subsubsection{Formula for exact correlations}\label{correlation-section}
We consider $m\in \{1,\ldots,L\}$ sites with coordinates $x_{1},\ldots,x_{m}\in \{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,m-1\}$. Each of these sites is occupied by $a_{k}\in\{1,\ldots,N-1\}$, we aim to compute

>>>>

%In this notation, the elements of the duality matrix reads
%\begin{equation}\label{ElementsDualityMatrixChain_1}
%	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
%\end{equation}
%\\
Using duality, one can compute the  $m$-point correlations between non-empty particles in terms of the absorption probabilities of $m$ dual particles. Therefore, to determine the non-equilibrium steady state correlations of the integrable multi-species stirring process, it is enough to compute these absorption probabilities.  %For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$. 
\begin{corollary}[Correlations via duality]
\label{prop-absorbing}
Consider $m\in \{1,\ldots,L\}$ and let $a_{k}\in\{1,\ldots,N-1\}$ species positioned at sites $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$. Then, the $m$-point correlations in the non-equilibrium steady state (NESS) read
\begin{equation}
\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m})
\end{equation}
where
\begin{equation}\label{absProbabilitiesIntegrable}
	\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\bm{\xi}\right)
\end{equation}
is the  probability that  $t_{k}$ dual particles of species $a_{k}$ (initially positioned at site $x_{k}$) are absorbed at the extra site $\{0\}$. The dual initial configuration is $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that 
\begin{equation}
\label{xsi-init}
	\begin{cases}
		\xi_{a}^{x}=1\qquad \text{if}\;x=x_{k}\;\text{and}\; a=a_{k}\\
		\xi_{a}^{x}=0\qquad \text{otherwise}
	\end{cases}
\end{equation}
\end{corollary}
\textbf{Proof}:
For any $\bm{\tau}\in \Omega^{'}$ the duality matrix defined in \eqref{ElementsDualityMatrixChain_1} evaluated on the dual configuration $\bm{\xi}\in\widetilde{\Omega}$ given in \eqref{xsi-init} read
\begin{equation}
	D(\bm{\tau},\bm{\xi})%=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{x_{k}},a_{k}}=1\}}
	=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\dt
\end{equation}
Therefore, by duality and ergodicity we have 
\begin{equation}\label{CorrelationByABS-prob}
	\begin{split}
\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_{1},\ldots,x_{m}}(t_{1},\ldots,t_{m})\dt
\end{split}
\end{equation}
\begin{flushright}
	$\square$
\end{flushright} 
    \begin{corollary}
ADD
\end{corollary}

@@

\begin{theorem}[Correlations in the non-equilibrium steady state]\label{thm-correlations}

@@

	\langle W|\widetilde{X}_{N}^{n}|V\rangle&=\langle W|\widetilde{X}_{N}\widetilde{X}_{N}^{n-1}|V\rangle=\langle W|\widetilde{X}_{N}^{n-1}|V\rangle +\langle W|\frac{1}{(\alpha_{a}-\beta_{a})}\widetilde{X}_{a}\widetilde{X}_{N}^{n-1}|V\rangle

@@

	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}=\frac{\Gamma(2+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})}{\Gamma(1+\sum_{j=x}^{L}\delta_{\tau_{j},N})}

@@

=&\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\frac{\Gamma(2+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})}{\Gamma(1+\sum_{j=x}^{L}\delta_{\tau_{j},N})}\nonumber\\

@@

		\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\langle \bm{\tau}|S_{2}^{-1}|\Psi^{''}\rangle\nonumber\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\frac{1}{(L+1)!}\prod_{x=1}^L\left((\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\right)\left[ \delta_{\tau_x,\sigma_x}+\beta_{\tau_x} \delta_{N,\sigma_x} (1-\delta_{\tau_x,N})\right]%\\&= \Psi^{''}(\bm{\tau})+\sum_{q_{1}= 1}^{L}(1-\delta_{\tau_{q_{1}},N})\Psi^{''}(\tau_{1},\ldots,\underbrace{N}_{q_{1}},\ldots,\tau_{L})\beta_{\tau_{q_{1}}}\\&+

@@

\begin{remark} By changeing the summation indices from $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}^{'}\in \{0,1-\delta_{\tau_{x},N}\}$ and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as 

@@

	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) =\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x_{j}},N})\right)

@@

\subsubsection{Formula for correlations}\label{correlation-section}
We consider $m\in \{1,\ldots,L\}$ sites with coordinates $x_{1},\ldots,x_{m}\in \{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,m-1\}$.We fix $a_{k}\in\{1,\ldots,N-1\}$ and we would like to compute
